---
title: "R Notebook"
output: html_notebook
---
```{r}

library(margins)
library(fpp2)
library(forecast)
library(readxl)
library(plyr)
library(lubridate)
```


```{r}
features <- read.csv2("data/stocks_most_important_features_bit_pos.csv", sep = ",")

price <- read.csv2("data/BTC-USD.csv", sep=",")

names(features)[names(features) == "date"] <- "Date"

features
price
```
'''

'''
```{r Joining data}

#data <- merge(data, price, by = "Date", type = "left", match = "all")
data <- merge(features,price,by="Date")


#format(data$ratio..t.1., digits=2, nsmall=2)

#exporttab <- merge(x=data, y=price, by.x='Date', by.y='Date', fill=-9999)
sapply(data, class)

data$ratio..t.1. = as.numeric(as.character(data$ratio..t.1.))
data$ratio..t.2. = as.numeric(as.character(data$ratio..t.2.))
data$ratio..t.6. = as.numeric(as.character(data$ratio..t.6.))
data$negatives..t.2. = as.numeric(as.character(data$negatives..t.2.))
data$negatives..t.3. = as.numeric(as.character(data$negatives..t.3.))
data$positives..t.5. = as.numeric(as.character(data$positives..t.5.))
data$Open = as.numeric(as.character(data$Open))
data$High = as.numeric(as.character(data$High))
data$Close = as.numeric(as.character(data$Close))
data$Adj.Close = as.numeric(as.character(data$Adj.Close))
data$Low= as.numeric(as.character(data$Low))


data$Date = as.Date(data$Date)

data

```

```{r}
# save a numeric vector containing 72 monthly observations
# from Jan 2009 to Dec 2014 as a time series object
myts <- ts(data[,3:14], start = c(2018, 1), end = c(2019, 124), deltat = 1/365) 

# subset the time series (June 2014 to December 2014)
#myts2 <- window(myts, start=c(2014, 6), end=c(2014, 12)) 
#myts <
#head(myts)

#mts <- as.numeric(time(myts[,0]))
#mts
```

```{r}
autoplot(myts,facets=TRUE)
```

```{r}
myts %>%
  as.data.frame() %>%
  ggplot(aes(x = ratio..t.6., y = Close)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)
(fit_r6 <- tslm(Close ~ ratio..t.6., data = myts))


myts %>%
  as.data.frame() %>%
  ggplot(aes(x = ratio..t.2., y = Close)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)
(fit_r2 <- tslm(Close ~ ratio..t.2., data = myts))



myts %>%
  as.data.frame() %>%
  ggplot(aes(x = ratio..t.1., y = Close)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)
(fit_r1 <- tslm(Close ~ ratio..t.1., data = myts))



myts %>%
  as.data.frame() %>%
  ggplot(aes(x = negatives..t.3., y = Close)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)
(fit_n3 <- tslm(Close ~ negatives..t.3., data = myts))

myts %>%
  as.data.frame() %>%
  ggplot(aes(x = negatives..t.2., y = Close)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)
(fit_n2 <- tslm(Close ~ negatives..t.2., data = myts))


myts %>%
  as.data.frame() %>%
  ggplot(aes(x = positives..t.5., y = Close)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)
(fit_p5 <- tslm(Close ~ positives..t.5., data = myts))


myts %>%
  as.data.frame() %>%
  ggplot(aes(x = Volume, y = Close)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE)
(fit_v <- tslm(Close ~ Volume, data = myts))
```
```{r}
checkresiduals(fit_n2)
```

In most cases, the p-values associated with the coefficients will be too small, and so some predictor variables will appear to be important when they are not. This is known as "spurious regression".


An important consideration when estimating a regression with ARMA errors is that all of the variables in the model must first be stationary. Thus, we first have to check that  

y_t and all of the predictors (x1_t,)

 appear to be stationary. If we estimate the model when any of these are non-stationary, the estimated coefficients will not be consistent estimates (and therefore may not be meaningful).
