---
title: "R Notebook"
output: html_notebook
---
```{r}

library(margins)
library(fpp2)
library(forecast)
library(readxl)
library(plyr)
library(lubridate)
```


```{r}
features <- read.csv2("data/stocks_most_important_features.csv", sep = ",")

price <- read.csv2("data/BTC-USD.csv", sep=",")

names(features)[names(features) == "date"] <- "Date"

features
price
```

```{r Joining data}

#data <- merge(data, price, by = "Date", type = "left", match = "all")
data <- merge(features,price,by="Date")

#exporttab <- merge(x=data, y=price, by.x='Date', by.y='Date', fill=-9999)


data

```

```{r}
# save a numeric vector containing 72 monthly observations
# from Jan 2009 to Dec 2014 as a time series object
myts <- ts(data, start=c(2018, 1), end=c(2019, 5), frequency=365) 

# subset the time series (June 2014 to December 2014)
#myts2 <- window(myts, start=c(2014, 6), end=c(2014, 12)) 
myts2 <- ts(data, start = decimal_date(as.Date("2018-01-02")), frequency = 365)
# plot series
myts2
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
